Extreme Value Chapter 3

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Figure 1 is ready and in the word document now

# Figure 1 - the mixture scenarios considered

@@

top_row <- fig1_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)

@@

# Histogram plus the points in the tail.
truth_df %>%
  ggplot(., aes(x = x_samps)) +
  geom_histogram(bins = 100) +
  geom_point(data = tru_tail[1:50,], aes(x = values, y = y), color = "black", alpha = 0.5) +
  labs(y = "Frequency", x = "Distance") +
  #lims(x = c(0, 150)) +
  theme_minimal() -> truth_hist
# truth_hist

# Density curve for the mixture based on the 50k samples.
truth_df %>%
  ggplot(., aes(x = x_samps)) +
  geom_density() +
  labs(y = "Density", x = "Distance") +
  lims(x = c(0, 150), y = c(0,0.05)) +
  theme_minimal() -> truth_density
# truth_density

@@

bottom_row <- plot_grid(truth_hist, truth_density)

plot_grid(top_row, bottom_row,nrow = 2)

@@

@@

```{r}
thetas %>% 
  knitr::kable()
```

>>>>

# Figure 1

@@

# Build the densities for plotting
weighted_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm, args = list(meanlog = pars$meanlog[y], sdlog = pars$sdlog[y]), color = dens_cols[y], size=1, alpha = 0.8))

# Plot density components of the mixture
ggplot() +
  weighted_densities +
  theme_bw(base_size = 7) +
  labs(y = "Component Densities") +
  lims(x = c(0, 150)) -> densities_plot

# Plot the means and sd for each of the curves
data.frame(desired_means, desired_sds, gID = factor(1:4)) %>%
  mutate(lo = desired_means - desired_sds,
         hi = desired_means + desired_sds) %>%
  ggplot(., aes(x = gID, y = desired_means, color = gID)) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = lo, ymax = hi), width = 0.1, size = 1) +
  scale_color_manual(values = dens_cols) +
  labs(y = "Mean +/- SD") +
  theme_bw(base_size = 7) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "none") -> means_sd_plot

@@

# Histogram plus the points in the tail.
truth_df %>%
  ggplot(., aes(x = x_samps)) +
  geom_histogram(bins = 100) +
  geom_point(data = tru_tail[1:50,], aes(x = values, y = y), color = "grey47", alpha = 0.9, size = 1) +
  geom_vline(xintercept = thresh_tests, color = dens_cols[4], linetype = "dashed", size = 0.3) +
  labs(y = "Frequency", x = "Distance") +
  #lims(x = c(0, 150)) +
  theme_bw(base_size = 7) -> truth_hist
# truth_hist

# Density curve for the mixture based on the 50k samples.
truth_df %>%
  ggplot(., aes(x = x_samps)) +
  geom_density() +
  labs(y = "Mixture Density", x = "Distance") +
  lims(x = c(0, 150), y = c(0,0.05)) +
  theme_bw(base_size = 7) +
  theme(axis.title.x = element_blank()) -> truth_density
# truth_density

@@

top_row <- plot_grid(means_sd_plot, densities_plot, truth_density, nrow = 1, rel_widths = c(1,2,2), labels = "AUTO", label_size = 8)

plot_grid(top_row, truth_hist, nrow = 2, labels = c("", "D"), label_size = 8)
ggsave("Ch3_samplesize/Figures/Figure1.png")

@@

# Table 1

@@

```{r}
thetas %>% 
  knitr::kable()
write.csv(thetas, file = "Ch3_samplesize/Figures/table1.csv")
```
